The Atala PRISM Protocol

### 2022-11-11 prism-backend/research/prism-protocol/did_atala.tex
Some work on UC-security of Atala DID.

    \begin{minipage}[t]{0.5\textwidth}
      \procedure[linenumbering]{$\pcif \cmd = \uccmd{KeyGen} \land \arg =
        \emptyset$}{
        \pccomment{\fbox{Key Generation}} \\
        \pcif \sid = (P,\ssid): \\
        \pcind \ucsend~(\uccmd{KeyGen},\sid)~\text{to}~\adv \\
        \pcind \ucrecv~(\uccmd{VerKey},\sid,v)~\text{from}~\adv \\
        \pcind \ucio{Output}~(\uccmd{VerKey},\sid,v)~\text{to}~P \\
        \pcind \text{Store}~(P,v)
      }
      \vspace*{0.25em}
      \procedure[linenumbering]{$\pcif \cmd = \uccmd{Verify} \land
        \arg = (\sig,\msg,v')$}{
        \pccomment{\fbox{Verify a message}} \\
        \ucsend~(\uccmd{Verify},\sid,\msg,\sig,v)~\text{to}~\adv \\
        \ucrecv~(\uccmd{Verified},\sid,\msg,\phi)~\text{from}~\adv \\
        \pcif v' = v \land (\msg,\sig,v,1) \in \SIG: f \gets 1 \\
        \pcelse \pcif v' = v \land P~\text{is not corrupt}~\land \\
        \pcind (\msg,\sig',v,1) \notin \SIG: \\
        \pcind \SIG \gets \SIG \cup \lbrace (\msg,\sig,v,0) \rbrace;
        f \gets 0 \\
        \pcelse \pcif (\msg,\sig,v',f') \in \SIG: f \gets f' \\
        \pcelse: \\
        \pcind \SIG \gets \SIG \cup \lbrace (\msg,\sig,v',\phi) \rbrace;~
        f \gets \phi \\
        \ucio{Output}~(\uccmd{Verified},\sid,\msg,f)
      }
    \end{minipage}
    \begin{minipage}[t]{0.5\textwidth}
      \procedure[linenumbering]{$\pcif \cmd = \uccmd{Sign} \land \arg = \msg$}{
        \pccomment{\fbox{Sign a message}} \\
        \pcif \sid = (P,\ssid) \\
        \pcind \ucsend~(\uccmd{Sign},\sid,\msg)~\text{to}~\adv \\
        \pcind \ucrecv~(\uccmd{Sig.},\sid,\msg,\sig)~\text{from}~
        \adv \\
        \pcind \pcif (\msg,\sig,v,0) \in \SIG: \\
        \pcind \pcind \ucio{Output}~(\uccmd{Error}) \\
        \pcind \pcelse: \\
        \pcind \pcind \SIG \gets \SIG \cup (\msg,\sig,v,1) \\
        \pcind \pcind \ucio{Output}~(\uccmd{Sig.},\sid,\msg,\sig)
      }
    \end{minipage}
  \end{framed}
  \caption{Ideal signature functionality, \IdealFSig, from \cite{canetti03}.}
  \label{fig:faobb}
\end{figure}

@@

@@

    \scalebox{0.9}{
      \begin{minipage}[t]{0.55\textwidth}
        \procedure[linenumbering]{$\pcif \cmd = \uccmd{Create} \land \arg =
          \lbrace (i,\lbl_i) \rbrace_{i\in[n]}$}{
          \pccomment{\fbox{DID Create operation}} \\
          \ucsend~(\uccmd{Create}, \sid, \arg)~\text{to}~\adv \\
          \ucrecv~(\uccmd{CreateOk}, \sid, did,
          \lbrace (i, \val_i) \rbrace_{i\in[n]}) \\
          \pcind \text{from}~\adv \\
          \pcif (P,\did,\cdot) \notin \DID \land
          \P(\lbrace (i, \lbl_i) \rbrace_{i\in[n]}) = 1: \\
          \pcind \DID \gets \DID \cup \lbrace (P,did,\lbrace
          (i,\lbl_i,\val_i) \rbrace_{i\in[n]}) \rbrace \\
          \ucio{Output}~(\uccmd{Created},\sid,\did,
          \lbrace (i,\val_i) \rbrace_{i\in[n]})
        }
      \end{minipage}
    }
    \scalebox{0.9}{
      \begin{minipage}[t]{0.5\textwidth}
        \procedure[linenumbering]{$\pcif \cmd = \uccmd{Read} \land
          \arg = did$}{
          \pccomment{\fbox{DID Read operation}} \\
          \ucsend~(\uccmd{Read},\sid,\arg)~\text{to}~\adv \\
          \ucrecv~(\uccmd{ReadOk},\sid)~\text{from}~\adv \\
          \pcif (\cdot,did,\sval) \in \DID: \\
          \pcind \ucio{Output}~(\uccmd{Read},\sid,(did,\sval))~\text{to}~P \\
          \pcelse: \\
          \pcind \ucio{Output}~(\uccmd{Read},\sid,\bot)~\text{to}~P    
        }    
      \end{minipage}
    }
    \vspace*{0.25em} \\
    \scalebox{0.9}{
      \begin{minipage}[t]{0.55\textwidth}
        \procedure[linenumbering]{$\pcif \cmd = \uccmd{Update} \land
          \arg = (did, \lbrace (i,\lbl_i) \rbrace_{i\in[n]})$}{      
          \pccomment{\fbox{DID Update operation}} \\
          \ucsend~(\uccmd{Update}, \sid, \arg)~\text{to}~\adv \\
          \ucrecv~(\uccmd{UpdateOk},\sid,
          \lbrace (i,\val_i) \rbrace_{i\in[n]}) \\
          \pcind \text{from}~\adv \\
          \pcif (P,did,\sval) \in \DID \land
          \P(\lbrace (i,\lbl_i) \rbrace_{i\in[n]}) = 1: \\
          \pcind \DID \gets \DID \setminus \lbrace (P,did,\sval) \rbrace~\cup \\
          \hspace*{7em} \lbrace (P, did,
          \lbrace (i,\lbl_i,\val_i) \rbrace_{i\in[n]}) \rbrace \\
          \ucio{Output}~(\uccmd{Updated},\sid,
          (\did,\lbrace (i,\val_i) \rbrace_{i\in[n]}))
        }
      \end{minipage}
    }
    \scalebox{0.9}{
      \begin{minipage}[t]{0.5\textwidth}
        \procedure[linenumbering]{$\pcif \cmd = \uccmd{Deact} \land \arg =
          (did, \lbrace (i,\lbl_i) \rbrace_{i\in[n]})$}{
          \pccomment{\fbox{DID Deactivate operation}} \\
          \ucsend~(\uccmd{Deact}, \sid, \arg)~\text{to}~\adv \\
          \ucrecv~(\uccmd{DeactOk},\sid)~\text{from}~\adv \\
          \pcif (P,did,\sval) \in \DID~\land \\
          \pcind \lbrace (i,\lbl_i) \rbrace_{i\in[n]} \subseteq \LBL(\sval): \\
          \pcind \sval' \gets \sval \setminus \lbrace (i,\lbl_i,\cdot)
          \rbrace_{i\in[n]} \\
          \pcind \pcif \P(\sval') = 1: \\
          \pcind \pcind \DID \gets \DID \setminus \lbrace (P,did,\sval) \rbrace~\cup \\
          \hspace*{8em}\lbrace (P,did,\sval') \rbrace \\
          \ucio{Output}~(\uccmd{Deacted},\sid,(\did,\sval'))
        }
      \end{minipage}
    }
  \end{framed}
  \caption{Ideal DID-based PKI functionality, \IdealFPKIDID.}
  \label{fig:fpkidid}
\end{figure}

@@

\begin{figure}[ht!]
  \begin{framed}
    \scalebox{0.9}{
      \begin{minipage}[t]{0.55\textwidth}
        \procedure[linenumbering=on]{$\pcif \cmd = \uccmd{Create} \land \arg =
          \lbrace (i,\lbl_i) \rbrace_{i\in[n]}$}{
          \pcif \exists i~\suchthat~\lbl_i \notin [\MasterKey,\AuthKey,
          \CommKey,\IssueKey] \lor
          \nexists i~\suchthat~\lbl_i = \MasterKey: \\
          \pcind \texttt{abort} \\
          \st \gets \emptyset \\
          \pcfor i \in [n]: \\
          \pcind \sid' \gets (P,\sid,i) \\
          \pcind \ucsend~(\uccmd{KeyGen},\sid')~\text{to}~\IdealFSig \\
          \pcind \ucrecv~(\uccmd{VerKey},\sid',\pk_i)~\text{from}~
          \IdealFSig \\
          \pcind \st \gets \st \cup \lbrace (i,\lbl_i,\pk_i) \rbrace \\
          \ucsend~(\uccmd{Hash},\st)~\text{to}~\IdealFRO \\
          \ucrecv~(\uccmd{Hashed},\st,h)~\text{from}~\IdealFRO \\
          \did \gets ``did:prism:''||~h \\
          \tx \gets (\texttt{CreateDID}, \did, \st) \\
          \text{Let}~j\in[n]~\text{be the least value s.t.}~\lbl_j = \MasterKey \\
          \ucsend~(\uccmd{Sign},(P,\sid,j),\tx)~\text{to}~\IdealFSig \\
          \ucrecv~(\uccmd{Sig.},(P,\sid,j),\tx,\sig)~\text{from}~\IdealFSig \\
          \ucsend~(\uccmd{Append},(\msg,\sig))~\text{to}~\IdealFaobb \\
          \ucio{Output}~(\uccmd{Created},\sid,\did,\lbrace \pk_i \rbrace_{i\in[n]})
        }
      \end{minipage}
    }
    \scalebox{0.9}{
      \begin{minipage}[t]{0.5\textwidth}
        \procedure[linenumbering=on]{$\pcif \cmd = \uccmd{Read} \land
          \arg = did$}{
          \ucsend~(\uccmd{Retrieve})~\texttt{to}~\IdealFaobb \\
          \ucrecv~(\uccmd{Retrieve},L)~\texttt{from}~\IdealFaobb \\
          \st \gets \emptyset \\
          L_{\did} \gets (\ast,\did,\ast) \subseteq \DID \\
          \pcfor (\tx=(\texttt{op},\did,\cdot),\sig) \in L_{\did}: \\
          \pcind \pk \gets \emptyset \\
          \pcind \pcif \texttt{op} = \texttt{CreateDID}~\land \\
          \pcind \pcind \text{no \texttt{CreateDID} appeared before}: \\
          \pcind \pcind (\cdot,\cdot,\lbrace (i,\lbl_i,\pk_i)
          \rbrace_{i\in[n]}) \gets \tx \\
          \pcind \pcind \st \gets \lbrace (i,\lbl_i,\pk_i) \rbrace_{i \in [n]} \\
          \pcind \pcind j \gets \LMKI(\st); \pk \gets \pk_j \\
          \pcind \pcif \texttt{op} = \texttt{UpdateDID}: \\
          \pcind \pcind (\cdot,\cdot,(\st_{del},\st_{add})) \gets \tx \\
          \pcind \pcind \lbrace i \rbrace_{i\in[n]} \gets \st_{del} \\ 
          \pcind \pcind \lbrace (i,\lbl_i,\pk_i) \rbrace_{i\in[\tilde{n}]} \gets \st_{add} \\
          \pcind \pcind j \gets \LMKI(\st); \pk \gets \pk_j \\
          \pcind \pcind \st \gets \st \setminus \st_{del} \cup \st_{add} \\
          \pcind \pcif \pk = \emptyset: \text{abort} \\
          \pcind \ucsend~(\uccmd{Verify},(P,\sid),\tx,\sig,\pk)~\text{to}~\IdealFSig \\
          \pcind \ucrecv~(\uccmd{Verified},(P,\sid),\tx,b)~\text{from}~\IdealFSig \\
          \pcind \pcif b = 0: \text{abort} \\
          \ucio{Output}~(\uccmd{Read},\sid,(\did,\st))
        }    
      \end{minipage}
    }
  \end{framed}
  \caption{\texttt{Create} and \texttt{Read} operations in Atala
    PRISM DID-based PKI protocol, \RealPKIDIDAtala, realising \IdealFPKIDID
    in the $(\IdealFRO,\IdealFSig,\IdealFaobb)$-hybrid model.}
  \label{fig:atalapkidid1}
\end{figure}

\begin{figure}[ht!]
  \begin{framed}
    \scalebox{0.9}{
      \begin{minipage}[t]{\textwidth}
        \textrm{We assume that the party running
          \texttt{Update} and \texttt{Deactivate} operations has an up to date
          copy $(\did,\lbrace (i,\lbl_i,\pk_i) \rbrace_{i\in[n]})$ of the DID to
          modify. Otherwise, a \texttt{Read} operation needs to be run before.}
      \end{minipage}
    }
    \vspace*{0.5em}

    \scalebox{0.90}{          
      \begin{minipage}[t]{0.55\textwidth}
        \procedure[linenumbering=on]{$\pcif \cmd = \uccmd{Update} \land
          \arg = (did, \lbrace (i,\lbl_i) \rbrace_{i\in\tilde{N}\subseteq [\tilde{n}]})$}{
          \pcif \exists i~\suchthat~\lbl_i \notin [\MasterKey,\AuthKey,
          \CommKey,\IssueKey] \lor
          \nexists i~\suchthat~\lbl_i = \MasterKey: \\
          \pcind \texttt{abort} \\
          \st_{add} \gets \emptyset \\
          \pcfor i \in \tilde{N}~\suchthat~ i > n : \\
          \pcind \ucsend~(\uccmd{KeyGen},(P,\sid,i))~\text{to}~\IdealFSig \\
          \pcind \ucrecv~(\uccmd{VerKey},(P,\sid,i),\pk_i)~\text{from}~
          \IdealFSig \\
          \pcind \st_{add} \gets \st_{add} \cup \lbrace (i,\lbl_i,\pk_i) \rbrace \\
          \st_{del} \gets [n] \setminus \tilde{N} \\
          % \text{Locally store}~(\did,\lbrace (i,\lbl_i,\pk_i) \rbrace_{i\in[\tilde{n}]} \\
          \tx \gets (\texttt{UpdateDID}, \did, (\st_{del}, \st_{add})) \\
          j \gets \LMKI(\lbrace \lbl_i \rbrace_{i\in\tilde{N}}) \\
          \ucsend~(\uccmd{Sign},(P,\sid,j),\tx)~\text{to}~\IdealFSig \\
          \ucrecv~(\uccmd{Sig.},(P,\sid,j),\tx,\sig)~\text{from}~\IdealFSig \\
          \ucsend~(\uccmd{Append},(\msg,\sig))~\text{to}~\IdealFaobb \\
          \ucio{Output}~(\uccmd{Updated},\sid,\did,\lbrace \pk_i \rbrace_{i\in[\tilde{N}]})
        }
      \end{minipage}
    }
    \scalebox{0.9}{
      \begin{minipage}[t]{0.45\textwidth}
        \procedure[linenumbering=on]{$\pcif \cmd = \uccmd{Deact} \land \arg =
          (did, \lbrace (i,\lbl_i) \rbrace_{i\in N \subseteq[n]})$}{       
          \text{Run as a \texttt{Update} operation}
        }
      \end{minipage}
    }
  \end{framed}
  \caption{\texttt{Update} and \texttt{Deactivate} operations in Atala
    PRISM DID-based PKI protocol, \RealPKIDIDAtala, realising \IdealFPKIDID
    in the $(\IdealFRO,\IdealFSig,\IdealFaobb)$-hybrid model.}
  \label{fig:atalapkidid2}
\end{figure}

\subsection{Notes for Implementations}

@@

>>>>

    \begin{minipage}[t]{0.5\textwidth}
      \procedure[linenumbering]{$\pcif \cmd = \uccmd{KeyGen} \land \arg =
        \emptyset$}{
        \pccomment{\fbox{Key Generation}} \\
        \pcif \sid = (P,\ssid): \\
        \pcind \ucsend~(\uccmd{KeyGen},\sid)~\text{to}~\adv \\
        \pcind \ucrecv~(\uccmd{VerKey},\sid,v)~\text{from}~\adv \\
        \pcind \ucio{Output}~(\uccmd{VerKey},\sid,v)~\text{to}~P \\
        \pcind \text{Store}~(P,v)
      }
      \vspace*{0.25em}
      \procedure[linenumbering]{$\pcif \cmd = \uccmd{Verif} \land
        \arg = (\sig,\msg,v')$}{
        \pccomment{\fbox{Verify a message}} \\
        \ucsend~(\uccmd{Verif},\sid,\msg,\sig,v)~\text{to}~\adv \\
        \ucrecv~(\uccmd{Verifd},\sid,\msg,\phi)~\text{from}~\adv \\
        \pcif v' = v \land (\msg,\sig,v,1) \in \SIG: f \gets 1 \\
        \pcelse \pcif v' = v \land P~\text{is not corrupt}~\land \\
        \pcind (\msg,\sig',v,1) \notin \SIG: \\
        \pcind \SIG \gets \SIG \cup \lbrace (\msg,\sig,v,0) \rbrace;
        f \gets 0 \\
        \pcelse \pcif (\msg,\sig,v',f') \in \SIG: f \gets f' \\
        \pcelse: \\
        \pcind \SIG \gets \SIG \cup \lbrace (\msg,\sig,v',\phi) \rbrace;~
        f \gets \phi \\
        \ucio{Output}~(\uccmd{Verifd},\sid,\msg,f)
      }
    \end{minipage}
    \begin{minipage}[t]{0.5\textwidth}
      \procedure[linenumbering]{$\pcif \cmd = \uccmd{Sign} \land \arg = \msg$}{
        \pccomment{\fbox{Sign a message}} \\
        \pcif \sid = (P,\ssid) \\
        \pcind \ucsend~(\uccmd{Sign},\sid,\msg)~\text{to}~\adv \\
        \pcind \ucrecv~(\uccmd{Signed},\sid,\msg,\sig)~\text{from}~
        \adv \\
        \pcind \pcif (\msg,\sig,v,0) \in \SIG: \\
        \pcind \pcind \ucio{Output}~(\uccmd{Error}) \\
        \pcind \pcelse: \\
        \pcind \pcind \SIG \gets \SIG \cup (\msg,\sig,v,1) \\
        \pcind \pcind \ucio{Output}~(\uccmd{Signed},\sid,\msg,\sig)
      }
    \end{minipage}
  \end{framed}
  \caption{Ideal signature functionality, \IdealFSig, from \cite{canetti03}.}
  \label{fig:faobb}
\end{figure}

@@

\todo{Mention public delayed outputs.}

@@

    \scalebox{0.9}{
      \begin{minipage}[t]{0.55\textwidth}
        \procedure[linenumbering]{$\pcif \cmd = \uccmd{Create} \land \arg =
          \lbrace (i,\lbl_i) \rbrace_{i\in[n]}$}{
          \pccomment{\fbox{DID Create operation}} \\
          \pcif \P(\lbrace (i, \lbl_i) \rbrace_{i\in[n]}) = 0:
          \text{abort} \\
          \ucsend~(\uccmd{Create}, \sid, \arg)~\text{to}~\adv \\
          \ucrecv~(\uccmd{CreateOk}, \sid, did,
          \lbrace (i, \val_i) \rbrace_{i\in[n]}) \\
          \pcind \text{from}~\adv \\
          \pcif (\cdot,\did,\cdot) \notin \DID: \\
          \pcind \DID \gets \DID \cup \lbrace (P,did,\lbrace
          (i,\lbl_i,\val_i) \rbrace_{i\in[n]}) \rbrace \\
          \ucio{Output}~(\uccmd{Created},\sid,\did,
          \lbrace (i,\val_i) \rbrace_{i\in[n]})
        }
      \end{minipage}
    }
    \scalebox{0.9}{
      \begin{minipage}[t]{0.5\textwidth}
        \procedure[linenumbering]{$\pcif \cmd = \uccmd{Read} \land
          \arg = did$}{
          \pccomment{\fbox{DID Read operation}} \\
          \ucsend~(\uccmd{Read},\sid,\arg)~\text{to}~\adv \\
          \ucrecv~(\uccmd{ReadOk},\sid)~\text{from}~\adv \\
          \pcif (\cdot,did,\sval) \in \DID: \\
          \pcind \ucio{Output}~(\uccmd{Read},\sid,(did,\sval))~\text{to}~P \\
          \pcelse: \\
          \pcind \ucio{Output}~(\uccmd{Read},\sid,\bot)~\text{to}~P    
        }    
      \end{minipage}
    }
    \vspace*{0.25em} \\
    \scalebox{0.9}{
      \begin{minipage}[t]{0.55\textwidth}
        \procedure[linenumbering]{$\pcif \cmd = \uccmd{Update} \land
          \arg = (did, \lbrace (i,\lbl_i) \rbrace_{i\in[n]})$}{      
          \pccomment{\fbox{DID Update operation}} \\
          \pcif \P(\lbrace (i, \lbl_i) \rbrace_{i\in[n]}) = 0:
          \text{abort} \\
          \ucsend~(\uccmd{Update}, \sid, \arg)~\text{to}~\adv \\
          \ucrecv~(\uccmd{UpdateOk},\sid,
          \lbrace (i,\val_i) \rbrace_{i\in[n]}) \\
          \pcind \text{from}~\adv \\
          \pcif (P,did,\sval) \in \DID: \\
          \pcind \DID \gets \DID \setminus \lbrace (P,did,\sval) \rbrace~\cup \\
          \hspace*{7em} \lbrace (P, did,
          \lbrace (i,\lbl_i,\val_i) \rbrace_{i\in[n]}) \rbrace \\
          \ucio{Output}~(\uccmd{Updated},\sid,
          (\did,\lbrace (i,\val_i) \rbrace_{i\in[n]}))
        }
      \end{minipage}
    }
    \scalebox{0.9}{
      \begin{minipage}[t]{0.5\textwidth}
        \procedure[linenumbering]{$\pcif \cmd = \uccmd{Deact} \land \arg =
          (did, \lbrace (i,\lbl_i) \rbrace_{i\in[n]})$}{
          \pccomment{\fbox{DID Deactivate operation}} \\
          \ucsend~(\uccmd{Deact}, \sid, \arg)~\text{to}~\adv \\
          \ucrecv~(\uccmd{DeactOk},\sid)~\text{from}~\adv \\
          \pcif (P,did,\sval) \in \DID~\land \\
          \pcind \lbrace (i,\lbl_i) \rbrace_{i\in[n]} \subseteq \LBL(\sval): \\
          \pcind \sval' \gets \sval \setminus \lbrace (i,\lbl_i,\cdot)
          \rbrace_{i\in[n]} \\
          \pcind \pcif \P(\sval') = 1: \\
          \pcind \pcind \DID \gets \DID \setminus \lbrace (P,did,\sval) \rbrace~\cup \\
          \hspace*{8em}\lbrace (P,did,\sval') \rbrace \\
          \ucio{Output}~(\uccmd{Deacted},\sid,(\did,\sval'))
        }
      \end{minipage}
    }
  \end{framed}
  \caption{Ideal DID-based PKI functionality, \IdealFPKIDID.}
  \label{fig:fpkidid}
\end{figure}

@@

\begin{figure}[ht!]
  \begin{framed}

    \scalebox{0.9}{
      \begin{minipage}[t]{\textwidth}
        \textrm{Party $P$ running operation \cmd with arguments \arg, in
          session \sid.}
      \end{minipage}
    }
    \vspace*{0.5em}

    \scalebox{0.9}{
      \begin{minipage}[t]{0.55\textwidth}
        \procedure[linenumbering=on]{$\pcif \cmd = \uccmd{Create} \land \arg =
          \lbrace (i,\lbl_i) \rbrace_{i\in[n]}$}{
          \pcif \exists i~\suchthat~\lbl_i \notin [\MasterKey,\AuthKey,
          \CommKey,\IssueKey] \lor
          \nexists i~\suchthat~\lbl_i = \MasterKey: \\
          \pcind \texttt{abort} \\
          \st \gets \emptyset \\
          \pcfor i \in [n]: \\
          \pcind \sid' \gets ((P,i),\sid) \\
          \pcind \ucsend~(\uccmd{KeyGen},\sid')~\text{to}~\IdealFSig \\
          \pcind \ucrecv~(\uccmd{VerKey},\sid',\pk_i)~\text{from}~
          \IdealFSig \\
          \pcind \st \gets \st \cup \lbrace (i,\lbl_i,\pk_i) \rbrace \\
          \ucsend~(\uccmd{Hash},\st)~\text{to}~\IdealFRO \\
          \ucrecv~(\uccmd{Hashed},\st,h)~\text{from}~\IdealFRO \\
          \did \gets ``did:prism:''||~h \\
          \tx \gets (\texttt{CreateDID}, \did, \st) \\
          j \gets \LMKI(\st); \sid' \gets ((P,j),\sid) \\
          \ucsend~(\uccmd{Sign},\sid',\tx)~\text{to}~\IdealFSig \\
          \ucrecv~(\uccmd{Signed},\sid',\tx,\sig)~\text{from}~\IdealFSig \\
          \ucsend~(\uccmd{Append},(\msg,\sig))~\text{to}~\IdealFaobb \\
          \ucio{Output}~(\uccmd{Created},\sid,\did,\lbrace (i,\pk_i)
          \rbrace_{i\in[n]})
        }
      \end{minipage}
    }
    \scalebox{0.9}{
      \begin{minipage}[t]{0.5\textwidth}
        \procedure[linenumbering=on]{$\pcif \cmd = \uccmd{Read} \land
          \arg = did$}{
          \ucsend~(\uccmd{Retrieve})~\texttt{to}~\IdealFaobb \\
          \ucrecv~(\uccmd{Retrieve},L)~\texttt{from}~\IdealFaobb \\
          \st \gets \emptyset \\
          L_{\did} \gets (\ast,\did,\ast) \subseteq \DID \\
          \pcfor (\tx=(\texttt{op},\did,\cdot),\sig) \in L_{\did}: \\
          \pcind \pk \gets \emptyset \\
          \pcind \pcif \texttt{op} = \texttt{CreateDID}~\land \\
          \pcind \pcind \text{no \texttt{CreateDID} appeared before}: \\
          \pcind \pcind (\cdot,\cdot,\lbrace (i,\lbl_i,\pk_i)
          \rbrace_{i\in[n]}) \gets \tx \\
          \pcind \pcind \st \gets \lbrace (i,\lbl_i,\pk_i) \rbrace_{i \in [n]} \\
          \pcind \pcind j \gets \LMKI(\st); \pk \gets \pk_j \\
          \pcind \pcif \texttt{op} = \texttt{UpdateDID}: \\
          \pcind \pcind (\cdot,\cdot,(\st_{del},\st_{add})) \gets \tx \\
          \pcind \pcind \lbrace i \rbrace_{i\in[n]} \gets \st_{del} \\ 
          \pcind \pcind \lbrace (i,\lbl_i,\pk_i) \rbrace_{i\in[\tilde{n}]} \gets \st_{add} \\
          \pcind \pcind j \gets \LMKI(\st); \pk \gets \pk_j \\
          \pcind \pcind \st \gets \st \setminus \st_{del} \cup \st_{add} \\
          \pcind \pcif \pk = \emptyset: \text{abort}; \pcelse \sid' \gets (P, \sid) \\
          \pcind \ucsend~(\uccmd{Verif},\sid',\tx,\sig,\pk)~\text{to}~\IdealFSig \\
          \pcind \ucrecv~(\uccmd{Verifd},\sid',\tx,b)~\text{from}~\IdealFSig \\
          \pcind \pcif b = 0: \text{abort} \\
          \ucio{Output}~(\uccmd{Read},\sid,(\did,\st))
        }    
      \end{minipage}
    }
  \end{framed}
  \caption{\texttt{Create} and \texttt{Read} operations in Atala
    PRISM DID-based PKI protocol, \RealPKIDIDAtala, realising \IdealFPKIDID
    in the $(\IdealFRO,\IdealFSig,\IdealFaobb)$-hybrid model.}
  \label{fig:atalapkidid1}
\end{figure}

\begin{figure}[ht!]
  \begin{framed}
    \scalebox{0.9}{
      \begin{minipage}[t]{\textwidth}
        \textrm{Party $P$ running operation \cmd with arguments \arg, in
          session \sid.} \\
        \textrm{We assume that the party running
          \texttt{Update} and \texttt{Deactivate} operations has an up to date
          copy $(\did,\lbrace (i,\lbl_i,\pk_i) \rbrace_{i\in[n]})$ of the DID to
          modify. Otherwise, a \texttt{Read} operation needs to be run before.}
      \end{minipage}
    }
    \vspace*{0.5em}

    \scalebox{0.90}{          
      \begin{minipage}[t]{0.55\textwidth}
        \procedure[linenumbering=on]{$\pcif \cmd = \uccmd{Update} \land
          \arg = (did, \lbrace (i,\lbl_i) \rbrace_{i\in\tilde{N}\subseteq [\tilde{n}]})$}{
          \pcif \exists i~\suchthat~\lbl_i \notin [\MasterKey,\AuthKey,
          \CommKey,\IssueKey] \lor
          \nexists i~\suchthat~\lbl_i = \MasterKey: \\
          \pcind \texttt{abort} \\
          \st_{add} \gets \emptyset \\
          \pcfor i \in \tilde{N}~\suchthat~ i > n : \\
          \pcind \ucsend~(\uccmd{KeyGen},((P,i),\sid))~\text{to}~\IdealFSig \\
          \pcind \ucrecv~(\uccmd{VerKey},((P,i),\sid),\pk_i)~\text{from}~
          \IdealFSig \\
          \pcind \st_{add} \gets \st_{add} \cup \lbrace (i,\lbl_i,\pk_i) \rbrace \\
          \st_{del} \gets [n] \setminus \tilde{N} \\
          % \text{Locally store}~(\did,\lbrace (i,\lbl_i,\pk_i) \rbrace_{i\in[\tilde{n}]} \\
          \tx \gets (\texttt{UpdateDID}, \did, (\st_{del}, \st_{add})) \\
          j \gets \LMKI(\lbrace \lbl_i \rbrace_{i\in\tilde{N}}) \\
          \ucsend~(\uccmd{Sign},((P,j),\sid),\tx)~\text{to}~\IdealFSig \\
          \ucrecv~(\uccmd{Signed},((P,j),\sid),\tx,\sig)~\text{from}~\IdealFSig \\
          \ucsend~(\uccmd{Append},(\msg,\sig))~\text{to}~\IdealFaobb \\
          \ucio{Output}~(\uccmd{Updated},\sid,\did,\lbrace \pk_i \rbrace_{i\in[\tilde{N}]})
        }
      \end{minipage}
    }
    \scalebox{0.9}{
      \begin{minipage}[t]{0.45\textwidth}
        \procedure[linenumbering=on]{$\pcif \cmd = \uccmd{Deact} \land \arg =
          (did, \lbrace (i,\lbl_i) \rbrace_{i\in N \subseteq[n]})$}{       
          \text{Run as a \texttt{Update} operation}
        }
      \end{minipage}
    }
  \end{framed}
  \caption{\texttt{Update} and \texttt{Deactivate} operations in Atala
    PRISM DID-based PKI protocol, \RealPKIDIDAtala, realising \IdealFPKIDID
    in the $(\IdealFRO,\IdealFSig,\IdealFaobb)$-hybrid model.}
  \label{fig:atalapkidid2}
\end{figure}

\subsubsection{Notes for Implementations.} %

@@

\subsection{Security of \RealPKIDIDAtala}
\label{ssec:sec-didatala}

\todo{Define $\P_{Atala}$}

\begin{theorem}[UC-security of \RealPKIDIDAtala]
  \label{thm:sec-didatala}
  \RealPKIDIDAtala UC-realizes $\IdealFPKIDID^{\P_{Atala}}$ in the $(\IdealFRO,
  \IdealFSig, \IdealFaobb)$-hybrid model.
\end{theorem}

\begin{proof}
  We show that \RealPKIDIDAtala UC-realizes \IdealFPKIDID, when configured
  with policy $\P_{Atala}$. For this, we give a simulator \Sim such that, for
  any environment \Env, $\Exec_{\RealPKIDIDAtala\adv,\Env} \approx
  \Exec_{\phiDIDAtala,\Sim,\Env}$,
  where \phiDIDAtala is a protocol composed with the same parties as
  \RealPKIDIDAtala but where each party is simply a dummy party that forwards
  any incoming/outgoing message to the ideal functionality \IdealFPKIDID. The
  simulator \Sim runs internally a copy of the real-world adversary \adv, as
  well as the ideal functionalities \IdealFRO, \IdealFSig and \IdealFaobb,
  and any involved party.

  \begin{description}
  \item[Simulating DID Create.] %
    %
    % Policy check
    \todo{Policy check not needed by \Sim, right?}
    When \Sim receives a message $(\uccmd{Create},\sid,\lbrace (i,\lbl_i)
    \rbrace_{i\in[n]})$ from a (dummy) party $P$, it simulates for \adv~the key
    generation process of $n$ signing key pairs, by sending $n$
    $(\uccmd{KeyGen},((P,i),\sid))$ queries to \adv~on
    behalf of \IdealFSig, and receiving the $n$ corresponding $(\uccmd{VerKey},
    ((P,i),\sid),\pk_i)$ responses.
    %
    % Hash computation
    \Sim then concatenates all $(i,\lbl_i,\pk_i)$ tuples into \st, and simulates
    a query to \IdealFRO \todo{do we need programmability or something?}, to set
    \did as ``$did:prism: h$'' as DID value.
    %
    % Tx sim
    With the DID value, \Sim simulates for \adv~the preparation of transaction
    \tx. That is, \Sim uses the master key with lower index, $j \gets
    \LMKI(\st)$, and simulates a query $(\uccmd{Sign},((P,j),\sid),\tx)$ to
    \IdealFSig, obtaining from \adv~$(\uccmd{Signed},((P,j),\sid),\tx,\sig)$.
    %
    % BB append
    \Sim also simulates appending the $(\tx,\sig)$ tuple to the bulletin board,
    by sending $(\uccmd{Append},(\tx,\sig))$ to \adv~on behalf of \IdealFaobb.
    %
    % Output
    Finally, \Sim sends the $(\uccmd{CreateOk},\sid,\did,\lbrace (i,\pk_i)
    \rbrace_{i\in[n]})$ to \IdealFPKIDID.
    Note that \did is generated uniformly at random. Thus, the probability that
    \IdealFPKIDID halts because $\did \in \DID$ is negligible, and \IdealFPKIDID
    outputs $(\uccmd{Created},\sid,\did,\lbrace (i,\val_i) \rbrace_{i\in[n]})$
    to \Sim.
  \item[Simulating DID Read.]
  \item[Simulating DID Update.] 
  \item[Simulating DID Deactivate.] Directly follows from DID Update.      
  \end{description}
\end{proof}
